Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-09 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Added...
prop_letter.tex Updating here and there...

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
is another one, where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.
This is the case where the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
can be applied and will be explained in the next paragraph.

@@

It asserts that there exists no function~$v$~\footnote{\yutsung{Kochen-Specker's original paper~\cite{kochenspecker1967}
used $\mathcal{E}$, but the Stanford Encyclopedia of Philosophy~\cite{Held2016}
used $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

>>>>

While mapping to $\mathscr{I}_{\infty}$ is one extreme case of quantum
IVPM, mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
is another one corresponding to the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}.

@@

It asserts that there exists no function~$v$~\footnote{\yutsung{Kochen-Specker's original paper~\cite{kochenspecker1967}
used $\mathcal{E}$, but the Stanford Encyclopedia of Philosophy~\cite{Held2016}
used $v$. I think it is less confusion to use $v$ here.}} assigning definite values to all observables such that for any sequence
of commuting observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

@@

\paragraph{Contextuality Inequality}

Cabello proved some inequalities to verify contextuality~\cite{Cabello_2008},
and we want to adopt these inequalities into our setting.

First, notice that his inequality (4)
